---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

**1. Download the data**

```{r}
url<- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(url,"Activity_monitoring_data.zip")
unzip("Activity_monitoring_data.zip")
data<- read.csv("activity.csv")
```

```{r}
head(data)
dim(data)
str(data)
summary(data)
```

**2. Process/transform the data**
```{r}
data$date<-as.Date(data$date)
```

```{r}
str(data)
```

## What is mean total number of steps taken per day?

**1. Library the required packages**

```{r}
library(tidyr)
library(ggplot2)
library(dplyr)
```

**2. Process/transform the data**

```{r}
daily_data <- split(data, data$date)
```

```{r}
length(daily_data)
```

```{r}
daily_total_step <- sapply(daily_data, function(x){
    sum(x[, "steps"])
})
```

***Total number of steps taken per day***

```{r}
Total_number_daily <- as.data.frame(daily_total_step)
Day<- rownames(Total_number_daily)
Total_number_daily<- cbind(Total_number_daily,Day)

```

***Histogram of the total number of steps taken each day***

```{r}
g<- ggplot(data=Total_number_daily, aes(x=daily_total_step, fill=Day))

g+geom_histogram(col="gray")+labs(title="Histogram of the total number of steps taken each day")+
        theme(legend.key.size=unit(.2,"inches"))
```

***Mean and median of the total number of steps taken per day***

```{r}
Mean_total_per_day<- mean(Total_number_daily$daily_total_step, na.rm = TRUE)
paste("Mean:", Mean_total_per_day)
```

```{r}
Median_total_per_day<- median(Total_number_daily$daily_total_step, na.rm = TRUE)
paste("Median:", Median_total_per_day)
```

## What is the average daily activity pattern?

***Time series plot***

```{r}
split_interval_data<-split(data,data$interval)

Average_steps<- sapply(split_interval_data, function(x){
        mean(x[, "steps"], na.rm = TRUE)
})

Average_steps<-as.data.frame(Average_steps)
interval<-as.numeric(row.names(Average_steps))
Average_steps<-cbind(Average_steps,interval)

g<-ggplot(Average_steps,aes(x=interval, y=Average_steps))
g+geom_line()+labs(title = "Average daily activity pattern")+xlab("Interval")
```

***Interval-835 contains the maximum number of steps.***

```{r}
max_interval<-max(Average_steps$Average_steps)
subset(Average_steps,Average_steps==max_interval)
```

## Imputing missing values

***Total number of missing values in the dataset***

```{r}
sum(is.na(data$steps))
```

***Filling in all of the missing values using mean of that day***

```{r}
replacebymean<-function(x){
        replace(x, is.na(x),mean(x, na.rm = TRUE))
}

data_tb<-tbl_df(data)
data_impute<-data_tb %>% group_by(interval) %>% mutate(steps=replacebymean(steps))
data_impute
```

***Histogram of the total number of steps taken each day ***

```{r}
impute_daily_data<-split(data_impute, data_impute$date)

impute_daily_total_step <- sapply(impute_daily_data, function(x){
    sum(x[, "steps"])
})

impute_Total_number_daily <- as.data.frame(impute_daily_total_step)
Date_impute<- rownames(impute_Total_number_daily)
impute_Total_number_daily<- cbind(impute_Total_number_daily,as.Date(Date_impute))

g<- ggplot(impute_Total_number_daily, aes(x=impute_daily_total_step, fill=Date_impute))

g+geom_histogram(col="gray", bins = 20)+labs(title="Histogram of the total number of steps taken each day")+
        theme(legend.key.size=unit(.15,"inches"))
```

***Mean and median total number of steps taken per day***

```{r}
Mean_total_per_day<- mean(Total_number_daily$daily_total_step, na.rm = TRUE)
paste("Old_Mean:", Mean_total_per_day)

impute_Mean_total_per_day<- mean(impute_Total_number_daily$impute_daily_total_step, na.rm = TRUE)
paste("impute_Mean", impute_Mean_total_per_day)
```

```{r}
Median_total_per_day<- median(Total_number_daily$daily_total_step, na.rm = TRUE)
paste("Old_Median:", Median_total_per_day)

impute_Median_total_per_day<- median(impute_Total_number_daily$impute_daily_total_step, na.rm = TRUE)
paste("impute_Median", impute_Median_total_per_day)
```

***Do these values differ from the estimates from the first part of the assignment? What is the impact of imputing missing data on the estimates of the total daily number of steps?***

The old mean and old median are almost same with the imputing mean and median.

## Are there differences in activity patterns between weekdays and weekends?

```{r}
data_impute$date<-as.Date(data_impute$date)
data_impute$weekdays<- weekdays(data_impute$date)
data_impute$weekend <- ifelse(data_impute$weekdays=="星期六" | data_impute$weekdays=="星期日", "Weekend", "Weekday" )
meanweekday <-aggregate(data_impute$steps, by=list(data_impute$weekend, data_impute$interval), na.omit(mean))
names(meanweekday) <- c("weekend", "interval", "steps")
ggplot(meanweekday, aes(x=interval, y=steps, color=weekend)) + geom_line()+
     facet_grid(weekend ~.) + xlab("Interval") + ylab("Mean of Steps") +
     ggtitle("Comparison of Average Number of Steps in Each Interval")
```